%
% Segment 6 --- Conclusion (slides 19--20). Two split frames that bookend the
% talk: slide 19 answers the research question (visual callback to slide 3) and
% restates the three contributions; slide 20 is future work + a minimal thanks.
% \splitpos and the footer-white flag are stateful --- set inside the group and
% reset after it.
%

{
  \renewcommand{\sectionsubtitle}{The answer, and what comes next}
  \section{Conclusion}
}


{
\setbeamerfont{itemize/enumerate body}{size=\small} % template pins lists to \normalsize
\setlength{\splitpos}{0.55\paperwidth} % colored pane left, title shifts right
\leftfooterwhitetrue
\begin{frame}{The answer}
  \begin{columns}[T]
    \begin{textcolumn}
      \color{white}\large
      \textbf{Yes --- conditional.}

      \medskip
      A fleet sustains and grows itself after genesis \textbf{when its income
      covers the per-node rent.}
    \end{textcolumn}
    \begin{textcolumn}
      \small
      \textbf{Three contributions:}
      \begin{enumerate}
        \item \textbf{Engineering} --- first self-replicating economic agent that
          buys real infrastructure on an open market.
        \item \textbf{Method} --- unmodified production code against faithful
          Bitcoin + VPS-marketplace replicas.
        \item \textbf{Empirical} --- fleet dynamics and one heritable trait under
          selection: a prediction met, one disconfirmed.
      \end{enumerate}
    \end{textcolumn}
  \end{columns}
\end{frame}
}
\setlength{\splitpos}{0pt}\leftfooterwhitefalse % reset stateful split/footer


{
\setbeamerfont{itemize/enumerate body}{size=\small} % template pins lists to \normalsize
\setlength{\splitpos}{0.55\paperwidth} % colored pane left, title shifts right
\leftfooterwhitetrue
\begin{frame}{Future work}
  \begin{columns}[T]
    \begin{textcolumn}
      \color{white}
      {\Large\textbf{Thank you}}

      \medskip
      {\large Questions welcome}
    \end{textcolumn}
    \begin{textcolumn}
      \small
      \begin{itemize}
        \item A \textbf{payment incentive} --- make consumers fund seeding
          directly (the missing revenue layer the rest of the system already
          supports).
        \item \textbf{Decentralized moderation} --- resolve removal requests
          across a fleet with no central authority (prerequisite for
          user-contributed content).
        \item \textbf{Long drought, no node cap} --- to test the unconfirmed
          survival half of the caution hypothesis.
      \end{itemize}
    \end{textcolumn}
  \end{columns}
\end{frame}
}
\setlength{\splitpos}{0pt}\leftfooterwhitefalse % reset stateful split/footer
