% =====================================================================
% Segment 1 --- The question (defense slides 2--4). Template frames below
% are kept as a feature reference; new content is added above them.
% =====================================================================

{
  \renewcommand{\sectionsubtitle}{Distribution without an operator}
  \section{The question}
}


\begin{frame}{Centralized distribution is a single point of control}
  Mainstream content distribution concentrates operational control on one entity
  that owns both the hardware and the catalog.
  \begin{itemize}
    \item One operator decides what stays online; availability depends on its
      finances, its policies, and its legal exposure.
    \item Peer-to-peer protocols (BitTorrent, IPFS) distribute the \emph{data}
      across many nodes --- so takedown is hard --- but the \emph{hardware} is
      still owned and kept alive by humans.
  \end{itemize}

  \begin{alertblock}{The open gap}
    Can the \textbf{infrastructure layer itself} be operator-independent ---
    leasing and paying for its own hardware, with no human running it after genesis?
  \end{alertblock}
\end{frame}


{
  \setlength{\splitpos}{0.55\paperwidth} % colored pane left, title shifts right
  \leftfooterwhitetrue
  \begin{frame}{Research question}
    \begin{columns}[T]
      \begin{textcolumn}
        \color{white}\large
        Can a network of autonomous software agents, seeded by a single
        human-initiated genesis node and controlled only by inherited economic
        parameters, \textbf{survive} and \textbf{grow} without further human
        intervention?
      \end{textcolumn}
      \begin{textcolumn}
        Read as the hypothesis under test: two outcomes must \emph{both} hold ---
        \textcolor{tud Orange}{persistence} and \textcolor{tud Orange}{expansion}
        --- with control reduced to inherited parameters and no human in the loop
        after genesis.

        Falsifiable: the closed-system run is a prediction the data must meet.
      \end{textcolumn}
    \end{columns}
  \end{frame}
}
\setlength{\splitpos}{0pt}\leftfooterwhitefalse % reset stateful split/footer


{
\setbeamerfont{itemize/enumerate body}{size=\small} % template pins lists to \normalsize
\footerinfootnotestrue % full-reference footnotes -> move footer into footnote band
\begin{frame}{Where this sits scientifically}
  \small
  \begin{columns}[T, onlytextwidth]
    \begin{column}{0.48\textwidth}
      Prior self-replicators ran on \emph{simulated} resources:
      \begin{itemize}
        \item von Neumann's automata\cite{vonneumann} and Ray's
          \textbf{Tierra}\cite{tierra} --- organisms competing for simulated CPU
          and RAM.
        \item DAOs and autonomic computing (MAPE-K) --- decentralized control over
          virtual, quota-based resources.
      \end{itemize}

      \textcolor{tud Orange}{\textbf{Novelty:}} the first self-replicator on
      \textbf{real, market-bought infrastructure paid for with real money} ---
      each child is a leased VPS.
    \end{column}
    \begin{column}{0.48\textwidth}
      Three contributions:
      \begin{enumerate}
        \item \textbf{Engineering} --- first self-replicating economic agent that
          buys real infrastructure on an open market.
        \item \textbf{Method} --- unmodified production code run against a replica
          Bitcoin network and a mock VPS marketplace.
        \item \textbf{Empirical} --- fleet dynamics and one heritable trait under
          selection: a prediction met, one disconfirmed.
      \end{enumerate}
    \end{column}
  \end{columns}
\end{frame}
}
